maxent model avec xvalidation (year-based test training)

### 2019-04-30 src/maxent_avec_xvalidation.Rmd
plots by depth...

stsum <- sum(binaryavgstack, na.rm = TRUE)
  writeRaster(stsum, (paste0("../output/maxent/predictions/", mthna, "/binary_sum_", mthna, ".asc")), overwrite=TRUE)
  sumplot <- plot(stsum, png(paste0("../output/maxent/predictions/", mthna, "/binary_sum_", mthna, ".png"))) 
  dev.off()
stavg <- calc(binaryavgstack, fun = mean, na.rm = TRUE)
  writeRaster(stavg, (paste0("../output/maxent/predictions/", mthna, "/binary_avg_", mthna, ".asc")), overwrite=TRUE)
  avgplot <- plot(stavg, png(paste0("../output/maxent/predictions/", mthna, "/binary_avg_", mthna, ".png"))) 
  dev.off()

>>>>

stsum <- sum(binaryavgstack, na.rm = TRUE)
  writeRaster(stsum, (paste0("../output/maxent/predictions/", mthna, "/binary_sum_", mthna, ".asc")), overwrite=TRUE)
  sumplot <- plot(stsum, png(paste0("../output/maxent/predictions/", mthna, "/binary_sum_", mthna, ".png"))) 
  dev.off()
stavg <- calc(binaryavgstack, fun = mean, na.rm = TRUE)
  writeRaster(stavg, (paste0("../output/maxent/predictions/", mthna, "/binary_avg_", mthna, ".asc")), overwrite=TRUE)
  avgplot <- plot(stavg, png(paste0("../output/maxent/predictions/", mthna, "/binary_avg_", mthna, ".png"))) 
  dev.off()
```

#plots by depth

first need some statistcs... for each layer how many cells have a value of 1...

```{r}
test <- cellStats(binaryavgstack[[30]], sum)
test
```
